DSIA 2017: Data Systems for Interactive Analysis

### 2017-02-23 2017/paper.tex
last revision of dsia 2017

\title{DSIA: Data Systems for Interactive Analysis}

@@

Beyond DSIA in 2015, here have been previous workshops in VIS that have investigated issues of large data visualization, such as LDAV. 
Our focus is markedly different from that of LDAV. 
While LDAV focuses on simulation and imaging data, we believe current backend techniques in information visualization and visual analytics are close to hitting a ceiling in terms of performance. 
We propose this workshop as a venue to discuss these limits, and fundamental new ways to attack them.

@@

\section{Format, Length, and Planned Activities}
We propose a half-day workshop that focuses on generating discussions between VIS and database researchers. 
The workshop will solicit submissions of position papers as well as short research papers from both the VIS and database communities. 
These papers will be reviewed by the organizing team. 
The authors of the selected top papers will be invited to each give a short presentation of their work (or position).

@@

\begin{itemize}
  \item Date of participation: Sunday, Monday, or Tuesday (Oct 1st,
    2nd, or 3rd)
  \item Submission Deadline: July 15th.
  \item Notification Deadline: August 1st.
\end{itemize}

@@

\paragraph*{Remco Chang} is an Associate Professor in the Computer Science Department at Tufts University. He received his BS from Johns Hopkins University in 1997 in Computer Science and Economics, MSc from Brown University in 2000, and PhD in computer science from UNC Charlotte in 2009. Prior to his PhD, he worked for Boeing developing real-time flight tracking and visualization software, followed by a position at UNC Charlotte as a research scientist. His current research interests include visual analytics, information visualization, HCI, and databases. His research has been funded by NSF, DHS, MIT Lincoln Lab, and Draper. He received the NSF CAREER Award in 2015.

>>>>

\title{DSIA 2017: Data Systems for Interactive Analysis}

@@

Beyond DSIA in 2015, there have been previous workshops in VIS that have investigated issues of large data visualization, such as LDAV. 
Our focus is markedly different from that of LDAV. 
While LDAV focuses on simulation and imaging data, we believe current backend techniques in information visualization and visual analytics are close to hitting a ceiling in terms of performance. 
We propose this workshop as a venue to discuss these limits, and fundamental new ways to attack them.

@@

\section{Format, Length, and Planned Activities}
We propose a \textbf{half-day workshop} that focuses on generating discussions between VIS and database researchers. 
The workshop will solicit submissions of position papers as well as short research papers from both the VIS and database communities. 
These papers will be reviewed by the organizing team. 
The authors of the selected top papers will be invited to each give a short presentation of their work (or position).

\begin{center}
\begin{tabular}{ l l } 
 \hline
 Schedule & Event \\ 
 \hline
 8:30  & Welcome and Introduction\\ 
 8:45 & Invited Keynote Speaker\\ 
 9:30 & Paper Session 1\\ 
 10:10 & Coffee Break \\ 
 10:30  & Paper Session 2\\ 
 11:30  & Panel Discussion\\ 
 12:00 & Closing\\
 12:10 & Lunch Break\\
 \hline
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{ l l } 
 \hline
 Date & Event \\ 
 \hline
  Date of Participation & Sunday (Oct 1st), or \\
					& Monday (Oct 2nd), or \\
					& Tuesday (Oct 3rd)\\
  Submission Deadline & July 15th \\
  Notification Date & August 1st\\
  Camera-Ready Deadline & August 15th\\
  USB Proceeding Deadline & August 25th\\
 \hline
\end{tabular}
\end{center}

%\begin{itemize}
%  \item Date of participation: Sunday, Monday, or Tuesday (Oct 1st,
%    2nd, or 3rd)
%  \item Submission Deadline: July 15th.
%  \item Notification Deadline: August 1st.
%  \item 
%\end{itemize}

@@

\paragraph*{Remco Chang} is an Associate Professor in the Computer Science Department at Tufts University. He received his BS from Johns Hopkins University in 1997 in Computer Science and Economics, MSc from Brown University in 2000, and PhD in computer science from UNC Charlotte in 2009. Prior to his PhD, he worked for Boeing developing real-time flight tracking and visualization software, followed by a position at UNC Charlotte as a research scientist. His current research interests include visual analytics, information visualization, HCI, and databases. His research has been funded by NSF, DARPA, DHS, MIT Lincoln Lab, and Draper. He received the NSF CAREER Award in 2015.
